---
title: "About the workshop"
---

The five participating Intermountain Region Inventory and Monitoring networks include:

* Northern Colorado Plateau Network (NCPN)
* Greater Yellowstone Network (GRYN)
* Southern Colorado Plateau Network (SCPN)
* Rocky Mountain Network (ROMN)
* Chihuahuan Desert Network (CHDN)
<br><br>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
```

```{r}
# Read the chunk (does not run the code).
knitr::read_chunk(file.path(PROJ_ROOT, 'map.R'))
```

<!-- ```{r} -->
<!-- # Run the chunk. -->
<!-- <<leaflet_map>> -->
<!-- ``` -->

## Survey design elements (Reynolds et al. 2012)
### Membership design: how locations are selected
#### Spatially-balanced sampling
##### Balanced acceptance sampling (BAS; Robertson et al. 2013)
[`SDraw`](https://github.com/tmcd82070/SDraw)

##### Generalized random tessellation stratified (GRTS; Stevens and Olsen 2003, 2004)
[`spsurvey`](https://github.com/cran/spsurvey) 

### Response design: what to measure and how
### Revisit design: schedule for visiting locations
